\chapter{Fundamentals of Particle Physics}
 
The standard model of particle physics (SM) is a theoretical model that aims to describe the fundamental particles and their interactions. the SM is a quantum field theory(QFT) that describes the behaviour of particles as excitations of underlying fields. The quantisation of the fields gives rise to specific properties of the fundamental particles such as mass, spin, charge, and flavour quantum numbers. The SM incorporates three of the four fundamental forces: the strong force, the weak force, and the electromagnetic force that together describe all interactions between fundamental particles. The fundamental particle can be divided into two categories: fermions and bosons. Fermions are the constituents of matter and have a half-interger spin, meaning for each particle an anti-particle can exist with opposite conserved quantum numbers. Fermions in turn can be divided into two categories: quarks and leptons. Quarks are the particles that make up protons and neutrons, the building blocks of atomic nuclei, and thus interact trough the strong force. All quarks have different masses and flavour quantum numbers but share their charge: the up-type quarks have 2/3 elementary charge and the down-type quarks have -1/3 elementary charge.  Leptons, on the other hand, do not interact trough the strong interaction and consist of three charged leptons\footnote{In the remainder of the thesis "leptons" is used to refer to charged leptons. Neutral leptons will be refered to by "neutrinos".}: electron, muon ,and tau particles and three charge-less leptons called neutrino's. The neutrinos are neutral particles that interact solely trough the weak force. Last, Bosons have an integer spin and are the mediators of the fundamental forces. There exist four types of bosons in the SM: the photon, two W bosons, the Z boson, and the gluon. Photons are the mediators of the electromagnetic force, responsible for interactions between charged particles. The QFT that describes the electromagnetic force is called Quantum electrodynamics(QED). The W- and Z-boson are mediators of the weak force and responsible for a known radioactive decay: the $\beta$-decay. Last, Gluons are the mediators of the strong force described by the QFT called  Quantum Chromodynamics (QCD). In addition to these fundamental particles, the Standard Model includes the Higgs boson, which is responsible for giving mass to the fundamental particles. The Higgs boson is a scalar particle that is related to the Brout-Englert-Higgs(BEH) mechanism and plays an important role in describing electroweak unification in the SM.